Unbalanced Mallows Models for Optimizing Expensive Black-Box Permutation Problems

### 2020-10-27 paper/main.tex
fix sec 5

\subsubsection{Other settings}.  For simplicity, we use Kendall's $\tau$
distance~(Eq.~\ref{eq:kendall_decomp}) in all
experiments. Nevertheless,
\citet{ZaeStoFriFisNauBar2014} points out that CEGO performs best on the QAP
when using Hamming distance.  We plan to extend UMM to other distance measures.
In all experiments, we consider a maximum budget of $\FEmax=400$ evaluations of
the actual objective function. In a white-box context, state-of-the-art
algorithms for the problems considered here typically evaluate
thousands of solutions, thus, the budget considered
here for the black-box context is extremely limited.

@@

The \textbf{LOP} \ldots

@@

Describir como se generan las intancias de LOP: Ekhine

Describir las instancias: Ekhine

For the LOP, we generated synthetic instances of size $n=20$, $m=200$, $\phi\in\{0.5,0.7,0.9\}$\MANUEL{what is $m$ here? We already use $\FEmax$ for the budget, but we could change it. }

@@

\subsection{Setting the learning rate}
The first part of the experimental analysis concerns the {analyses} of the learning rate, which corresponds to parameter $\rho$ of uBorda. As stated in Section~\ref{sec:sampling}, $\rho$ is automatically set at each iteration in such a way that the $100r_1\%$ of the samples have the $100r_2\%$ of the weight. In this regard, we tried different configurations of parameters $r_1$ and $r_2$ in all the instances.\MANUEL{?? why did we try this values.} Figure~\ref{fig:heatmaps} shows the best solution\MANUEL{best solution found at the end of a run?} (averaged for 10 runs) for instances: \texttt{N-t1d100.01} and \texttt{N-t1d150.01} for the LOP, \texttt{reC05} for the PFSP, \texttt{kra32} for the QAP. This experiment for all the real datasets can be bound in the supplemental material. \MANUEL{The caption says synthetic instances}

\begin{figure}[htb]
  \centering%
  \includegraphics[width=0.24\textwidth]{../img/heatmap_N-t1d100_01}
  \includegraphics[width=0.24\textwidth]{../img/heatmap_N-t1d150_01}
  \includegraphics[width=0.24\textwidth]{../img/heatmap_rec05}
  \includegraphics[width=0.24\textwidth]{../img/heatmap_kra32_dat}
    \caption{Mean fitness  for different configuration for the learning rate \label{fig:heatmaps}}
\end{figure}

>>>>

\subsubsection{Other settings}.  For simplicity, we use Kendall's $\tau$
distance~(Eq.~\ref{eq:kendall_decomp}) in all
experiments. Nevertheless,
\citet{ZaeStoFriFisNauBar2014} points out that CEGO performs best on the QAP
when using Hamming distance.  We plan to extend UMM to other distance measures in the future.
In all experiments, we consider a maximum budget of $\FEmax=400$ evaluations of
the actual objective function. In a white-box context, state-of-the-art
algorithms for the problems considered here typically evaluate
thousands of solutions, thus, the budget considered
here for the black-box context is extremely limited.

@@

The \textbf{LOP} \ldots\EKHINE{Mío}

@@

For the LOP, we generated synthetic instances of size $n=20$, $m=200$, $\phi\in\{0.5,0.7,0.9\}$\MANUEL{what is $m$ here? We already use $\FEmax$ for the budget, but we could change it. }
Describir como se generan las intancias de LOP: Ekhine

Describir las LOPLIB instancias: Ekhine

@@

The first part of the experimental analysis concerns the {analyses} of the learning rate, which corresponds to parameter $\rho$ of uBorda. As stated in Section~\ref{sec:sampling}, $\rho$ is automatically set at each iteration in such a way that the $100r_1\%$ of the samples have the $100r_2\%$ of the weight. In this regard, we tried different configurations of parameters $r_1$ and $r_2$ in all the instances.\MANUEL{?? why did we try this values.} Figure~\ref{fig:heatmaps} shows the best solution\MANUEL{best solution found at the end of a run?} (averaged for 10 runs) for instances: \texttt{N-t1d100.01} and \texttt{N-t1d150.01} for the LOP, \texttt{reC05} for the PFSP, \texttt{kra32} for the QAP. This experiment for all the real datasets can be bound in the supplemental material. \MANUEL{The caption says synthetic instances}

\begin{figure}[htb]
  \centering%
  \begin{minipage}{0.49\linewidth}\centering
    \texttt{N-t1d100.01}\\[-0.2ex]
    \includegraphics[width=\textwidth]{../img/heatmap_N-t1d100_01}
  \end{minipage}
  \begin{minipage}{0.49\linewidth}\centering
    \texttt{N-t1d50.01}\\[-0.2ex]
 \includegraphics[width=\textwidth]{../img/heatmap_N-t1d150_01}
\end{minipage}\\
\includegraphics[width=0.49\textwidth]{../img/heatmap_rec05}
  \includegraphics[width=0.49\textwidth]{../img/heatmap_kra32_dat}
    \caption{Mean fitness  for different configuration for the learning rate \label{fig:heatmaps}}
\end{figure}
